Dummy classifier

### 2021-06-07 src/dummy_classifier.Rmd
Small change
Cleaned up code.

```{r}
df1 <- make_threshold_conversion_data_frame(125, -1) 
df2 <- make_threshold_conversion_data_frame(125, -0.1)
df <- bind_rows(`k=-1`=df1, `k=-0.1`= df2, .id="k")
df %>% ggplot(aes(x=Hb, y=Probability, color=k)) + geom_point() + scale_y_continuous(breaks=seq(0, 1, by=0.1)) + labs(colour="Logistic function parameter") + ggtitle("Female")
```

```{r}
df1 <- make_threshold_conversion_data_frame(135, -1) 
df2 <- make_threshold_conversion_data_frame(135, -0.1)
df <- bind_rows(`k=-1`=df1, `k=-0.1`= df2, .id="k")
df %>% ggplot(aes(x=Hb, y=Probability, color=k)) + geom_point() + scale_y_continuous(breaks=seq(0, 1, by=0.1)) + labs(colour="Logistic function parameter") + ggtitle("Male")
```

@@

```{r}
use_logistic_regression=TRUE
if (use_logistic_regression) {
  res <- dummy_predictor2(train_female, test_female)
  prediction_female <- res$result
  fit_female <- res$fit

  res <- dummy_predictor2(train_male, test_male)
  prediction_male <- res$result
  fit_male <- res$fit
} else {
  prediction_female <- dummy_predictor(validate_female, 125)  # or would mean Hb be better centering point than deferral threshold
  prediction_male <- dummy_predictor(validate_male, 135)
}
head(prediction_female)
head(prediction_male)
fit_male
fit_female
```

@@

```{r}
dummy_result <- suppressMessages(process_all_data(dummy2_ids, replicates=100))
```

@@

>>>>

```{r, eval=FALSE}
df1 <- make_threshold_conversion_data_frame(125, -1) 
df2 <- make_threshold_conversion_data_frame(125, -0.1)
df <- bind_rows(`k=-1`=df1, `k=-0.1`= df2, .id="k")
df %>% ggplot(aes(x=Hb, y=Probability, color=k)) + geom_point() + scale_y_continuous(breaks=seq(0, 1, by=0.1)) + labs(colour="Logistic function parameter") + ggtitle("Female")
```

```{r, eval=FALSE}
df1 <- make_threshold_conversion_data_frame(135, -1) 
df2 <- make_threshold_conversion_data_frame(135, -0.1)
df <- bind_rows(`k=-1`=df1, `k=-0.1`= df2, .id="k")
df %>% ggplot(aes(x=Hb, y=Probability, color=k)) + geom_point() + scale_y_continuous(breaks=seq(0, 1, by=0.1)) + labs(colour="Logistic function parameter") + ggtitle("Male")
```

@@

```{r}
use_logistic_regression=TRUE
if (use_logistic_regression) {
  res_female <- dummy_predictor2(train_female, test_female)
  prediction_female <- res_female$result
  fit_female <- res_female$fit

  res_male <- dummy_predictor2(train_male, test_male)
  prediction_male <- res_male$result
  fit_male <- res_male$fit
} else {  # Old way was to do it by hand using logistic function
  prediction_female <- dummy_predictor(validate_female, 125)  # or would mean Hb be better centering point than deferral threshold
  prediction_male <- dummy_predictor(validate_male, 135)
}
head(prediction_female)
head(prediction_male)
fit_male
fit_female
```

@@

```{r}
#dummy_result <- suppressMessages(process_all_data(dummy2_ids, replicates=100))
dummy_result <- suppressMessages(process_all_data(dummy2_ids))
```

@@

Compute the effects of applying baseline model. This needs still some cleanup.

```{r}
result_male <- res_male$result %>% mutate(prediction=as.factor(ifelse(Deferred>0.36, "Deferred", "Accepted")))
result_female <- res_female$result %>% mutate(prediction=as.factor(ifelse(Deferred>0.64, "Deferred", "Accepted")))
```

```{r}
summary(result_male)
```

```{r}
summary(result_female)
```

```{r}
nm <- nrow(result_male)
nf <- nrow(result_female)
md <- sum(result_male$obs=="Deferred")
fd <- sum(result_female$obs=="Deferred")
cat(sprintf("Men deferred %i (%.2f%%)\n", md, md/nm*100))
cat(sprintf("Women deferred %i (%.2f%%)\n", fd, fd/nf*100))

md2 <- sum(result_male$obs=="Deferred" & result_male$prediction=="Accepted")
fd2 <- sum(result_female$obs=="Deferred" & result_female$prediction=="Accepted")
cat(sprintf("Men deferred %i (%.2f%%)\n", md2, md2/nm*100))
cat(sprintf("Women deferred %i (%.2f%%)\n", fd2, fd2/nf*100))

```
```{r}
mextension <- sum(result_male$prediction=="Deferred")
fextension <- sum(result_female$prediction=="Deferred")
cat(sprintf("Men extended for 6 months %i (%.2f%%)\n", mextension, mextension/nm*100))
cat(sprintf("Women extended for 6 months %i (%.2f%%)\n", fextension, fextension/nf*100))
```
